Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-03-22 apj.tex
more simulation

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$1-5\times10^{-5}$
%------
confidence.
The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Extending the model to three color parameters gives almost identical results for
all the parameters in common,
plus a detection of a third parameter at
%--- table.py
$1-5\times10^{-4}$
%-----
confidence;
this new parameter represents supernova color diversity
beyond that tracked by the spectral features and two-parameter dust models.
\end{abstract}

@@

The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
\color{black}

\section{Supernova Model III: Fitzpatrick Dust}
\label{model0:sec}
\color{blue}
Dust models can explain the extrinsic magnitude and color variations found in
the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
terms predicted by a dust extinction model from the literature.  
%
%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
%except that dust
%is used in place of  the linear two-color-parameter  model.      
The dust model of  \citet{1999PASP..111...63F} is considered:
while commonly used dust
models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.

@@

>>>>

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The color changes allowed by the model are almost parallel to the color changes allowed by the dust model of  \citet{1999PASP..111...63F} with floating
total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced extinctions and color excess
are both qualitatively consistent with $R^F \sim 2.4$.
The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Inspired that our  two-parameter model, with no conditioning that would steer it toward a dust model, produces behavior similar to that expected from Galactic dust, we extend  the model to three color parameters.
In this new case we obtain consistent results for
all the parameters in common,
plus a detection of a third parameter at
%--- table.py
$(1-5\times10^{-4})$
%-----
confidence;
this new parameter represents supernova color diversity
beyond that tracked by the spectral features and two-parameter dust models.
A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
\end{abstract}

@@

\color{black}
The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
\color{blue}
We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered well
within the 68\% credible interval.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
the uncertainties in the predictor variable, which in turn lead to 
regression dilution.  Our analysis is susceptible to this bias because we do consciously do not include distributions
of supernova parameters as part of our model.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output23_sim/coeff0.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $U$ band of ten independent simulated data sets.  Lines show the values of the input values.
            \label{simglobal1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output23_sim/coeff1.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $B$ band of ten independent simulated data sets.   Lines show the values of the input values.
 \label{simglobal2:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5.2in]{output23_sim/coeff2.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $V$ band of ten independent simulated data sets.   Lines show the values of the input values.
 \label{simglobal3:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
      \includegraphics[width=5.2in]{output23_sim/coeff3.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $R$ band of ten independent simulated data sets.   Lines show the values of the input values.
\label{simglobal4:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
         \includegraphics[width=5.2in]{output23_sim/coeff4.pdf} 
            \caption{Aggregated Model~II posterior contours for $c$, $\alpha$, $\beta$, $\eta$, $\gamma^0$, $\gamma^1$,  $\delta$, and $\sigma$ in the $I$ band of ten independent simulated data sets.   Lines show the values of the input values.
 \label{simglobal5:fig}}
\end{figure}

\color{black}
\section{Supernova Model III: Fitzpatrick Dust}
\label{model0:sec}
\color{blue}
Dust models can explain the extrinsic magnitude and color variations found in
the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
terms predicted by a dust extinction model from the literature.  
%
%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
%except that dust
%is used in place of  the linear two-color-parameter  model.      
The dust model of  \citet{1999PASP..111...63F} is considered:
while commonly used dust
models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.

@@

\color{blue}
We stress that our $\delta$ vector does not capture the full behavior of the observable effects of the $D$ parameter, but rather only
the contribution perpendicular to the $\gamma$ vectors.
\color{black}
